Interfering with Noninterference \iftext\thanks{\bcp{Identify applicable funding agencies here (DARPA and NSF and...?)}}\fi

### 2020-01-17 main.tex
Reorganize to make things better

\bcp{Needs a parameter now.}

@@

% An {\em observer} $\observer \in CONTOURS \rightarrow (\MA \exists X.\; (\CONTOURS \rightarrow X) \times
% (X \rightarrow \CONTOURS) \times (\MACHS \times X \rightharpoonup \MACHS
% \times X) $
% comprises
% \begin{enumerate*}
%   \item a private type $X$,
%   \item a function taking a contour to an initial value of $X$, and
%   \item a function that allows ``reading off'' a contour from an $X$, and
%   \item a partial step function of type
%   $(\MACHS \times X) \rightharpoonup X$.
% \end{enumerate*}
\leo{The following all assumes lockstep-ness:}

\leo{I think we need variants from here... Should we call it
  indistinguishability?}

A {\em contoured hyperproperty} is a set of pairs of contoured
traces such that:
\begin{itemize}
\item {\em same-length:}

@@

  For every pair of traces $\overline{(C, M)}_n$ and $\overline{(C',
    M')}_n$ in the set, $C_i = C_i'$ for all $i<n$.

\item {\em prefix-closed:}

  For every pair of traces $\overline{(C, M)}_n$ and $\overline{(C,
    M')}_n$ in the set, the pair $\overline{(C, M)}_m$ and
  $\overline{(C, M')}_m$ is also in the set if $m < n$.

@@

  For every pair of traces $\overline{(C, M)}_n$ and $\overline{(C,
    M')}_n$ in the set, and for every $0 \leq i < n$, there exists in
  the set a pair of traces $\overline{(C', N)}_m$ and $\overline{(C',
    N')}_m$ such that $C_0' = C_i$, $N_0 = M_i$, and $N_0' = M_0'$.

@@

  For every pair of traces $\overline{(C, M)}$ and $\overline{(C,
    M')}$ in the set, and for every machine state $N_0$ such that
  $N_0$ is a variant of $M_0$, there exists in the set a pair of
  traces $\overline{(C, M)}_m$ and $\overline{(C, N)}_m$.

@@

  For every pair of traces $\overline{(C, M)}_n$ and $\overline{(C,
    M')}_n$ in the set, $C_0 \leq C_i$ for all $i<n$, where $C \leq
  C'$ if $\forall \component, C(\component) \leq C'(\component)$ and
  $\VIS < \HID$.

\end{itemize}
\iftext{} \bcp{Maybe prefix closed?}\fi.
% \bcp{Should we require that it contain all possible starting states and
%   contours (though of course the sequences can be singletons in many
%   cases!)?  What does it mean if it doesn't?}

@@

NI is the contoured hyperproperty where:
\begin{itemize}
\item For each pair of traces in the hyperproperty, all the contours
  coincide.
\item For each pair of traces in the hyperproperty, If the initial
  machine states plus contour are variants, then the observervations
  of the two traces coincide.
\end{itemize}

@@

Formally, a policy
%
$\pol \in \CONTOURS \rightarrow \MACHS \rightarrow \SEQ{\MACHS}$
%
takes a contour $\contour$ and a starting machine state $\mach_0$ and produces
a finite or infinite sequence of states $\mach_0,\,\mach_1 ,\, \ldots$ such
that $\mach_{i-1} \stepstounderfull \mach_i$ for each $i > 0$ in the sequence.

>>>>

@@

% An {\em observer} $\observer \in CONTOURS \rightarrow (\MA \exists X.\; (\CONTOURS \rightarrow X) \times
% (X \rightarrow \CONTOURS) \times (\MACHS \times X \rightharpoonup \MACHS
% \times X) $
% comprises
% \begin{enumerate*}
%   \item a private type $X$,
%   \item a function taking a contour to an initial value of $X$, and
%   \item a function that allows ``reading off'' a contour from an $X$, and
%   \item a partial step function of type
%   $(\MACHS \times X) \rightharpoonup X$.
% \end{enumerate*}

A {\em contoured hyperproperty} is a set of pairs of contoured
traces.

A {\em contoured lockstep-hyperproperty} is a contoured hyperproperty
such that:

\leo{Informally first, I don't like it too much:}
\begin{itemize}
\item each trace in every pair of a contoured trace in the set have the
  same length, and
\item each pair of elements in every pair of a contoured trace in the
  set have the same contour.
\end{itemize}

\leo{Formally:}
\begin{itemize}
\item {\em same-length:}

@@

  For every pair of traces $\overline{(C, M)}_n$ and $\overline{(C',
    M')}_n$ in the set, $C_i = C_i'$ for all $i<n$.
\end{itemize}

\leo{Indistinguishability/variations:}

\leo{Normal lockstep noninterference:}

(Lockstep-)Noninterference is the contoured lockstep hyperproperty
where:
\begin{itemize}
\item For each pair of traces in the hyperproperty, all the contours
  coincide.
\item For each pair of traces in the hyperproperty, If the initial
  machine states plus contour are variants, then the observervations
  of the two traces coincide.
\end{itemize}

\leo{Nested lockstep noninterference:}

Generalizing to allow for contours to change throughout the execution,
nested lockstep noninterference is the contoured lockstep
hyperproperty where:

\begin{itemize}
\item {\em prefix-closed:}

  For every pair of traces $\overline{(C, M)}_n$ and $\overline{(C,
    M')}_n$ in the set, the pair of truncated traces $\overline{(C,
    M)}_m$ and $\overline{(C, M')}_m$ is also in the set if $m < n$.

@@

  For every pair of traces $\overline{(C, M)}_n$ and $\overline{(C,
    M')}_n$ in the set, and for every $0 \leq i < n$, there exists in
  the set a pair of traces $\overline{(C', N)}_m$ and $\overline{(C',
    N')}_m$ such that $C_0' = C_i$, $N_0 = M_i$, and $N_0' = M_i'$.

@@

  For every pair of traces $\overline{(C, M)}_n$ and $\overline{(C,
    M')}_n$ in the set, and for every machine state $N_0$ such that
  $N_0$ is a variant of $M_0$, there exists in the set a pair of
  traces $\overline{(C, M)}_m$ and $\overline{(C, N)}_m$.

@@

  For every pair of traces $\overline{(C, M)}_n$ and $\overline{(C,
    M')}_n$ in the set, $C_0 \leq C_i$ for all $i<n$, where $C \leq
  C'$ if $\forall \component, C(\component) \leq C'(\component)$ and
  $\VIS < \HID$.
\end{itemize}

\leo{..and the observations of each trace coincide, right?}

% \bcp{Should we require that it contain all possible starting states and
%   contours (though of course the sequences can be singletons in many
%   cases!)?  What does it mean if it doesn't?}

@@

@@

\leo{Shouldn't this take a pair (C,M) to a pair (C,M)?}
Formally, a policy
%
$\pol \in \CONTOURS \rightarrow \MACHS \rightarrow \SEQ{\MACHS}$
%
takes a contour $\contour$ and a starting machine state $\mach_0$ and produces
a finite or infinite sequence of states $\mach_0,\,\mach_1 ,\, \ldots$ such
that $\mach_{i-1} \stepstounderfull \mach_i$ for each $i > 0$ in the sequence.
